---
title: "Environment Classification"
output:
    html_document:
        toc: true
        toc_depth: 3
        toc_float: true
        number_sections: true
        theme: cerulean
        highlight: pygments
        code_folding: hide
        fig_width: 9
        fig_height: 3
        css: style.css
params:
    datadir: "./data"
    graphdir: "./graphs"
    macrodir: "./macros"
    tabledir: "./tables"
---

```{r echo = FALSE, warning=FALSE, message=FALSE}
## https://bookdown.org/yihui/rmarkdown-cookbook/source-script.html
source("analysis.R", local = knitr::knit_global())
```

# Native Environments

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
## handle easy cases: call, package, and foreign
native_env <-
    native_env %>%
    rename(orig_fun_name = qual_name) %>%
    mutate(package_kind = package) %>%
    mutate(package = !is.na(package)) %>%
    mutate(category = case_when(call_env | dispatch ~ "Call",
                                package ~ "Package",
                                is.na(source_fun_name_1) ~ "Foreign",
                                TRUE ~ "Other")) %>%
    filter()                                

## handle S4 by looking at function definition
native_env <-
    native_env %>%
    left_join(select(functions, qual_name, fun_def), by = c("source_fun_name_1" = "qual_name")) %>%
    mutate(std_generic = str_detect(fun_def, "^new\\(\"standardGeneric\", "),
           non_std_generic = str_detect(fun_def, "^new\\(\"nonstandardGenericFunction\", ")) %>%
    mutate(source_fun_name_1 = case_when(std_generic | non_std_generic ~ "methods*$#$*new",
                                         TRUE ~ source_fun_name_1)) %>%
    select(-std_generic, -non_std_generic)
    
    
## manually handle special cases

other_env <-
    native_env %>%
    filter(category == "Other") %>%
    mutate(source_fun_name_1 = case_when(event_seq == "|substitute|" ~ "base*$#$*substitute",
                                         source_fun_name_1 == "<NA>*$#$*new" ~ "R6*$#$*generator_funs*$#$*new",
                                         source_fun_name_1 == "<NA>*$#$*e19df9d61bee0213c272516026ad08a38dd7032994489f386bcb9ec7200b95b5995a5a7467ba599f460b0bb10dbc55ff605f93269f3f3ec72614f38884fb8c99" ~ "iterators*$#$*makeIwrapper",
                                         source_fun_name_1 == "<NA>*$#$*3c35b2abb9250fb5e3a2af5c7a18bdc390b3454bee71eb0c0d0cc5fb5fb31949493df59a40660a7c816ed7a3f251dd26b93e3c88c9a920d3c0b7d07a10fe68d7" ~ "dplyr*$#$*DataMask*$#$*eval_all_mutate",
                                         TRUE ~ source_fun_name_1))
                                         
native_env <-
    native_env %>%
    filter(category != "Other") %>%
    bind_rows(other_env) %>%
    mutate(package = case_when(is.na(source_fun_name_1) ~ NA_character_,
                               TRUE ~ map_chr(str_split(source_fun_name_1, fixed("*$#$*")), ~.[1]))) %>%
    mutate(core = case_when(category == "Call" ~ TRUE,
                            category == "Package" ~ TRUE,
                            category == "Other" & is_core_package(package) ~ TRUE,
                            category == "Other" & !is_core_package(package) ~ FALSE,
                            TRUE ~ NA)) %>%
    mutate(native = TRUE) %>%
    mutate(primary_source = source_fun_name_1)
```

# New Environments


```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
new_env <-
    new_env %>%
    mutate(primary_source = case_when(str_starts(source_fun_name_1, fixed("base*$#$*lazyLoadDBexec")) ~ source_fun_name_1,
                                      str_starts(source_fun_name_2, fixed("base*$#$*lazyLoadDBexec")) ~ source_fun_name_2,
                                      str_starts(source_fun_name_2, fixed("base*$#$*loadNamespace")) ~ source_fun_name_2,
                                      source_fun_name_1 == "base*$#$*new.env" & is.na(source_fun_name_2) ~ "base*$#$*package_load_file",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*5d8ec22f1fac51fafcb0a876cc9a1dad489c1b41bfc4427f6634a9857d6e45a22b0c5a8504ee92c76d994698a2b00900888d4df7fa22d64c4e0196443f11c9b2" ~ "dplyr*$#$*dplyr_lazy_vec_chop_impl",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*24a2bd9ef1d1d0bed806a984c395ea21bbe8f6c7e28034d5ab619490dfd2057496cb2893ea5f506ca61e31d3580e8e2ed220a9fc53ee5970cabc102f8fd241eb" ~ "R6*$#$*R6Class",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*2ae04899b56d2a4922d9088b16dca9f5493c3ceb37dabbfb0d6625d23af95e73e9e212ac86b83f1445eacfdbd3fa81b3a661bb7f3c5da3fa04debfa085395681*$#$*make_first_new_slice" ~ "R6*$#$*make_first_new_slice",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*2ae04899b56d2a4922d9088b16dca9f5493c3ceb37dabbfb0d6625d23af95e73e9e212ac86b83f1445eacfdbd3fa81b3a661bb7f3c5da3fa04debfa085395681*$#$*make_new_slice" ~ "R6*$#$*make_new_slice",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*clone*$#$*make_new_slice" ~ "R6*$#$*make_new_slice",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*copy" ~ "lme4*$#$*merPredD*$#$*copy",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*829b877f5e7b68192afbd9af2c4c159e08a96ffb2169b846ab54cec6eab9b2122aee15552088cfbb79051662709544dd40cc1a037b3da266a43d372317870ab9" ~ "shiny*$#$*RestoreContext*$#$*reset",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*checkMatrix" ~ "Matrix*$#$*checkMatrix",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*new" ~ "R6*$#$*generator_funs*$#$*new",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*create_super_env" ~ "R6*$#$*create_super_env",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*clone*$#$*make_first_new_slice" ~ "R6*$#$*make_first_new_slice",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*initialize" ~ "R6*$#$*generator_funs*$#$*new",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*271ae2fa8d46b84c79a0b568c8ce6fb89fe66b0ad80a18be62ae15dcf13a1fd0701aaf43706e7c4bd694aa4f34c809f2551e010abff6210ed4fe8a8c3ac7980f" ~ "httpuv*$#$*AppWrapper*$#$*initialize",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*cad9f5e72cf80a892ad8cee6ac96c942739dbf25a9e519a0dbe833aaab59778cf815f838583bf8fb528a743bff410b0e1db9bfa2597a1d046c11111e2a1fcd70" ~ "methods*$#$*.InitMethodDefinitions*$#$*initialize",                                  
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*53f26b2cc4bd7c82af8e9821b32aefa979dab81840aaac8996db5353037c0ddc5f41064696a9181d13d0362cc7c6d3deed1fcc3da364a0db446ab271b90e4f08" ~ "shiny*$#$*shinyAppDir_serveR",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*moreSessionInfo" ~ "CLA*$#$*moreSessionInfo",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*5ee24a437c49708a0c574d944232c19f979e7bc53cbdeac097f0155a96b32aa49322aad1e26a9df50e9e9f3230a5b20f95616d31116f1e010eec4d1b9594a97a" ~ "dplyr*$#$*tests*$#$*testthat*$#$*test-across.R",                     
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*5ee24a437c49708a0c574d944232c19f979e7bc53cbdeac097f0155a96b32aa49322aad1e26a9df50e9e9f3230a5b20f95616d31116f1e010eec4d1b9594a97a" ~ "dplyr*$#$*tests*$#$*testthat*$#$*test-across.R",                        
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*c2fc402d1f015684f414ec363dfa3b4f339189c31f973af868049d096b5b1ac3d14ea80c1b6c7e00f1e90e533871e10dfefdf9f5c2c83303c17e6feb077bf8e5" ~ "R6*$#$*examples*$#$*CustomCloner",                                      
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*r_parse_eval" ~ "rlang*$#$*tests*$#$*testthat*$#$*helper-c-api.R",                    
                                      TRUE ~ source_fun_name_2)) %>%
    mutate(package = map_chr(str_split(primary_source, fixed("*$#$*")), ~.[1])) %>%
    # move nlme to base, it uses local function.
    mutate(package = if_else(package == "nlme", "base", package)) %>%
    mutate(core = is_core_package(package), native = FALSE)
```

# All Environments

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
all_env <-
    new_env %>%
    bind_rows(native_env) %>%
    mutate(category = case_when(str_starts(primary_source, fixed("base*$#$*lazyLoadDBexec")) ~ "Package",
                                str_starts(primary_source, fixed("base*$#$*loadNamespace")) ~ "Package",
                                str_starts(primary_source, fixed("base*$#$*package_load_file")) ~ "Package",
                                str_starts(primary_source, fixed("base*$#$*dyn.load")) ~ "Package",
                                TRUE ~ category))
    
env_source <-
    all_env %>%
    count(core, native, wt = count, name = "count") %>%
    arrange(desc(count)) %>%
    mutate(perc = compute_proportion(count, 6)) %>%
    mutate(count = label_number_si(accuracy = 0.1)(count),
           perc = label_percent(accuracy = 0.01)(perc))
    
datatable(env_source)

ENV_CATEGORY <-
    all_env %>%
    count(category, wt = count, name = "count") %>%
    arrange(desc(count)) %>%
    mutate(perc = compute_proportion(count, 6)) %>%
    mutate(count = label_number_si(accuracy = 0.1)(count),
           perc = label_percent(accuracy = 0.01)(perc))
           
datatable(ENV_CATEGORY)

ENV_CATEGORY %>%
pmap_chr(function(category, count, perc) {
    sprintf("%s&%s&%s", str_to_title(category), count, perc)
}) %>%
as_tex_table()
```

# Core Environments

## Native Core Environment Details

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}

native_env %>%
filter(core) %>%
count(native, category, package, wt = count, name = "count") %>%
arrange(desc(count)) %>%
    mutate(perc = compute_proportion(count, 6)) %>%
    mutate(count = label_number_si(accuracy = 0.1)(count),
           perc = label_percent(accuracy = 0.001)(perc)) %>%
datatable()
```

## R Core Environment Details

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}

new_env %>%
filter(core) %>%
count(native, package, wt = count, name = "count") %>%
arrange(desc(count)) %>%
    mutate(perc = compute_proportion(count, 6)) %>%
    mutate(count = label_number_si(accuracy = 0.1)(count),
           perc = label_percent(accuracy = 0.001)(perc)) %>%
datatable()
```

## Core Other Environments

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}

native_env %>%
    filter(core) %>%
    filter(category == "Other") %>%
    count(package, wt = count, name = "count") %>%
    datatable()

native_env %>%
    filter(core) %>%
    filter(category == "Other") %>%
    count(source_fun_name_1, wt = count, name = "count") %>%
    datatable()
## str(native_env)
## 
## other_env <-
##     native_env %>%
##     filter(category == "Other") %>%
##     mutate(source_fun_name_1 = case_when(str_starts(source_fun_name_1, fixed("vctrs*$#$*")) ~ "vctrs",
##                                          str_starts(source_fun_name_1, fixed("igraph*$#$*")) ~ "igraph",
##                                          str_starts(source_fun_name_1, fixed("Rcpp*$#$*")) ~ "Rcpp",
##                                          str_starts(source_fun_name_1, fixed("cli*$#$*")) ~ "cli",
##                                          str_starts(source_fun_name_1, fixed("magrittr*$#$*")) ~ "magrittr",
##                                          str_starts(source_fun_name_1, fixed("methods*$#$*")) ~ "methods",
##                                          str_starts(source_fun_name_1, fixed("lme4*$#$*")) ~ "lme4",
##                                          str_starts(source_fun_name_1, fixed("nlme*$#$*")) ~ "nlme",
##                                          str_starts(source_fun_name_1, fixed("base*$#$*")) ~ "base",
##                                          str_starts(source_fun_name_1, fixed("stats*$#$*")) ~ "stats",
##                                          str_starts(source_fun_name_1, fixed("grDevices*$#$*")) ~ "grDevices",
##                                          str_starts(source_fun_name_1, fixed("lattice*$#$*")) ~ "lattice",
##                                          str_starts(source_fun_name_1, fixed("tools*$#$*")) ~ "tools",
##                                          str_starts(source_fun_name_1, fixed("callr*$#$*")) ~ "callr",
##                                          str_starts(source_fun_name_1, fixed("plyr*$#$*")) ~ "plyr",
##                                          str_starts(source_fun_name_1, fixed("data.table*$#$*")) ~ "data.table",
##                                          str_starts(source_fun_name_1, fixed("ggplot2*$#$*")) ~ "ggplot2",
##                                          str_starts(source_fun_name_1, fixed("gtools*$#$*")) ~ "gtools",
##                                          str_starts(source_fun_name_1, fixed("cluster*$#$*")) ~ "cluster",
##                                          str_starts(source_fun_name_1, fixed("rlang*$#$*")) ~ "rlang",
##                                          TRUE ~ source_fun_name_1)) %>%
##     count(source_fun_name_1, wt = count, name = "count") %>%
##     arrange(desc(count)) %>%
##     mutate(perc = compute_proportion(count, 6)) %>%
##     mutate(cumperc = round(100 * cumsum(count)/sum(count), 2)) %>%
##     mutate(count = label_number_si(accuracy = 0.1)(count),
##            perc = label_percent(accuracy = 0.1)(perc))
## 
## datatable(other_env)
```

# Explicit Environments

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
process_event_seq <- function(df) {
    df <-
    df %>%
    mutate(orig_seq = event_seq) %>%
    mutate(event_seq = str_replace_all(event_seq, "\\^\\d\\|", "|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "\\^\\d\\d\\|", "|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "getNamespace\\|", "")) %>%
    mutate(event_seq = str_replace_all(event_seq, "as.environment_0\\|", "")) %>%
    mutate(event_seq = str_replace_all(event_seq, "globalenv_0\\|", "")) %>%
    mutate(event_seq = str_replace_all(event_seq, "baseenv_0\\|", "")) %>%
    mutate(event_seq = str_replace_all(event_seq, "parent.env_1\\|", "")) %>%
    mutate(event_seq = str_replace_all(event_seq, "Argument\\|", "")) %>%
    mutate(event_seq = str_replace_all(event_seq, "Return\\|", "")) %>%
    mutate(event_seq = str_replace_all(event_seq, "parent.env_0\\|", "")) %>%
    mutate(event_seq = str_replace_all(event_seq, "L\\|", "A|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "D\\|", "A|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "R\\|", "A|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "substitute\\|", "S|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "EvalEntryDirect\\|", "V|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "EvalExitDirect\\|", "")) %>%
    mutate(event_seq = str_replace_all(event_seq, "CallEntry\\|", "")) %>%
    mutate(event_seq = str_replace_all(event_seq, "CallExit\\|", "#|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "EvalEntryIndirect\\|", "V|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "EvalExitIndirect\\|", "")) %>%
    mutate(event_seq = str_replace_all(event_seq, "exists\\|", "A|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "new.env_0\\|", "N|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "new.env_1\\|", "!|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "parent.env<-_2\\|", "!|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "lockEnvironment_1\\|", "L|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "list2env_0\\|", "A|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "list2env_1\\|", "A|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "env2list_1\\|", "A|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "get0\\|", "A|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "mget\\|", "A|"))%>%
    mutate(event_seq = str_replace_all(event_seq, "get\\|", "A|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "assign\\|", "A|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "lockBinding_1\\|", "L|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "\\$\\|", "A|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "\\$<-\\|", "A|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "\\[\\[\\|", "A|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "\\[\\[<-\\|", "A|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "\\.subset2\\|", "A|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "\\|parent.env<-_0\\|parent.env<-_1\\|", "|parent.env<-_1|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "sys.frame_0\\|", "X|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "sys.frames_0\\|", "X|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "parent.frame_0\\|", "X|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "environment_0\\|", "X|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "environment<-_1\\|", "!|")) %>%
    mutate(event_seq = str_replace_all(event_seq, "parent.env<-_1\\|", "Z|")) %>%
    mutate(event_seq = str_trim(event_seq)) %>%
    mutate(event_seq = case_when(str_ends(event_seq, fixed("|#|")) ~ str_sub(event_seq, 1, -3),
                                 TRUE ~ event_seq)) %>%
    mutate(event_seq = str_trim(event_seq))

    df <-
    df %>%
    mutate(event_seq = map_chr(str_split(event_seq, fixed("|")),
                               function(events) {
                                   paste(sort(unique(str_trim(events))), collapse = " ")
                               })) %>%
    mutate(event_seq = str_trim(event_seq))
    df
}

```

## User Environments

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
USER_EXPLICIT_ENV <-
    all_env %>%
    filter(!core) %>%
    process_event_seq() %>%
    mutate(event_seq = case_when( event_seq == "" | event_seq == "A N V" | event_seq == "N V" ~ "N A V",
                                 event_seq == "N" | event_seq == "A N" | event_seq == "A" ~ "N A",
                                 event_seq == "! N" | event_seq == "! A N" ~ "N A !",
                                 event_seq == "@ N" | event_seq == "@ A N" ~ "N A @",
                                 event_seq == "! @ N" | event_seq == "! @ A N" ~ "N A @ !",
                                 TRUE ~ event_seq))

str(USER_EXPLICIT_ENV)

cat("Total Explicit User Environments: ", sum(USER_EXPLICIT_ENV$count))
```

### Packages

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
USER_EXPLICIT_ENV_PACKAGES  <-
    USER_EXPLICIT_ENV %>%
    count(package, wt = count, name = "count") %>%
    arrange(desc(count)) %>%
    mutate(cumperc = round(100 * cumsum(count)/ sum(count), 2)) %>%
    mutate(count = label_number_si(0.1)(count))

datatable(USER_EXPLICIT_ENV_PACKAGES)

USER_EXPLICIT_ENV_PACKAGES %>%
slice(1:14) %>%
pmap_chr(function(package, count, cumperc) {
    sprintf("\\code{%s}&%s&%.1f\\%%", package, count, cumperc)
}) %>%
as_tex_table()

cat("Total Explicit User Packages: ", nrow(USER_EXPLICIT_ENV_PACKAGES))
```

### Functions

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
USER_EXPLICIT_ENV_FUNCTIONS <-
    USER_EXPLICIT_ENV %>%
    count(primary_source, wt = count, name = "count") %>%
    arrange(desc(count)) %>%
    mutate(cumperc = round(100 * cumsum(count)/ sum(count), 2)) %>%
    mutate(count = label_number_si(0.1)(count))

datatable(USER_EXPLICIT_ENV_FUNCTIONS)

USER_EXPLICIT_ENV_FUNCTIONS %>%
slice(1:10) %>%
pmap_chr(function(primary_source, count, cumperc) {
    fun <- str_replace_all(primary_source, fixed("*$#$*"), "::")
    sprintf("\\code{%s}&%s&%.1f\\%%", fun, count, cumperc)
}) %>%
as_tex_table()

cat("Total Explicit User Functions: ", nrow(USER_EXPLICIT_ENV_FUNCTIONS))
```

### Parent Type

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
USER_EXPLICIT_ENV_PARENTS <-
    USER_EXPLICIT_ENV %>%
    count(native, parent_type, wt = count, name = "count")
    
datatable(USER_EXPLICIT_ENV_PARENTS)
```


### Event Sequence

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
USER_EXPLICIT_ENV_EVENT_SEQ <-
    USER_EXPLICIT_ENV %>%
    group_by(event_seq) %>%
    summarize(count = sum(count), package_count = length(unique(package)), packages = paste(unique(package), collapse="|")) %>%
    ungroup() %>%
    arrange(desc(count)) %>%
    mutate(cumperc = round(100 * cumsum(count)/ sum(count), 2))


USER_EXPLICIT_ENV_EVENT_SEQ %>%
    mutate(count = label_number_si(0.1)(count)) %>%
    mutate(package_count = label_number_si()(package_count)) %>%
    datatable()
    
USER_EXPLICIT_ENV_EVENT_SEQ %>%
    mutate(count = label_number_si(0.1)(count)) %>%
    mutate(package_count = label_number_si()(package_count)) %>%
slice(1:7) %>%
pmap_chr(function(event_seq, count, package_count, packages, cumperc) {
    sprintf("\\texttt{%s}&%s&%.1f\\%%", event_seq, count, cumperc)
}) %>%
as_tex_table()
```


### Formula

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
USER_EXPLICIT_ENV_FORMULA <-
    USER_EXPLICIT_ENV %>%
    filter(str_detect(event_seq, fixed("~"))) %>%
    count(primary_source, wt = count, name = "count")
    
datatable(USER_EXPLICIT_ENV_FORMULA)

cat("Total formula environments: ", sum(USER_EXPLICIT_ENV_FORMULA$count))
```

### Eval

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
USER_EXPLICIT_ENV_EVAL <-
    USER_EXPLICIT_ENV %>%
    mutate(eval_kind = case_when(str_detect(event_seq, fixed("V")) & str_detect(event_seq, fixed("U")) ~ "both",
                                 str_detect(event_seq, fixed("V")) ~ "direct",
                                 str_detect(event_seq, fixed("U")) ~ "indirect",
                                 TRUE ~ NA_character_)) %>%
    filter(!is.na(eval_kind)) %>%
    count(package, wt = count, name = "count") %>%
    arrange(desc(count)) %>%
    mutate(cumperc = round(100 * cumsum(count)/ sum(count), 2))
    
datatable(USER_EXPLICIT_ENV_EVAL)

cat("Total environments passed to eval: ", sum(USER_EXPLICIT_ENV_EVAL$count))
cat("% environments passed to eval: ", sum(USER_EXPLICIT_ENV_EVAL$count) / sum(USER_EXPLICIT_ENV_EVENT_SEQ$count))
```

### Class Attribute

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
USER_EXPLICIT_ENV_CLASS <-
    USER_EXPLICIT_ENV %>%
    filter(!is.na(class)) %>%
    mutate(kind = case_when(str_ends(class, fixed("ggproto|gg")) ~ "ggplot2::ggproto|gg",
                            str_ends(class, fixed("replot_xts|environment")) ~ "xts::replot_xts|environment",
                            str_ends(class, fixed("XMLHashTree|XMLAbstractDocument")) ~ "XML::XMLHashTree|XMLAbstractDocument",
                            str_ends(class, fixed("event_loop")) ~ "later::event_loop",
                            str_ends(class, fixed("rlang_ctxt_pronoun")) ~ "rlang::rlang_ctxt_pronoun",
                            str_ends(class, fixed("r6lite")) ~ "rlang::r6lite",
                            str_ends(class, fixed("idf|environment")) ~ "plyr::idf|environment",
                            class == "R6ClassGenerator" ~ "R6::R6ClassGenerator",
                            str_detect(class, fixed("session_proxy")) ~ "shiny::session_proxy",
                            str_detect(class, fixed("R6")) ~ "R6::R6",
                            TRUE ~ NA_character_)) %>%
    filter(!is.na(kind)) %>%
    count(kind, wt = count, name = "count") %>%
    arrange(desc(count)) %>%
    mutate(cumperc = round(100 * cumsum(count)/ sum(count), 2))

USER_EXPLICIT_ENV_CLASS %>%
mutate(count = label_number_si(0.1)(count)) %>%
datatable()

USER_EXPLICIT_ENV_CLASS %>%
mutate(count = label_number_si(0.1)(count)) %>%
pmap_chr(function(kind, count, cumperc) {
    splits <- str_split(kind, fixed("::"))[[1]] 
    package <- splits[1]
    classes <- splits[2]
    classes <- str_replace_all(classes, fixed("|"), " ")
    sprintf("\\texttt{%s}&\\texttt{%s}&%s&%.1f\\%%", package, classes, count, cumperc)
}) %>%
as_tex_table()

cat("Total environments with attributes: ", sum(USER_EXPLICIT_ENV_CLASS$count))
cat("% environments with attributes: ", sum(USER_EXPLICIT_ENV_CLASS$count) / sum(USER_EXPLICIT_ENV_EVENT_SEQ$count))
```

## Core Environments

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}

cat("Total core explicit envs", sum(filter(all_env, core, is.na(category) | category == "Other")$count))

CORE_EXPLICIT_ENV <-
    all_env %>%
    filter(core) %>%
    filter(is.na(category) | category == "Other") %>%
    filter(!str_starts(primary_source, fixed("base*$#$*lazyLoadDBexec"))) %>%
    filter(!str_starts(primary_source, fixed("base*$#$*loadNamespace"))) %>%
    filter(!str_starts(primary_source, fixed("base*$#$*package_load_file"))) %>%
    filter(!str_starts(primary_source, fixed("base*$#$*dyn.load"))) %>%
    #filter(is.na(category) | category == "other") %>%
    #filter(!(primary_source %in% c("base*$#$*lazyLoadDBexec*$#$*mkenv", "base*$#$*loadNamespace*$#$*makeNamespace", "base*$#$*package_load_file"))) %>%
    #filter(!str_starts(primary_source, fixed("base*$#$*lazyLoadDBexec*$#$*"))) %>%
    #filter(!str_starts(primary_source, fixed("base*$#$*loadNamespace*$#$*"))) %>%
    process_event_seq() %>%
    mutate(event_seq = case_when(primary_source == "base*$#$*eval" | primary_source == "base*$#$*evalq" ~ "A V",
                                 event_seq == "" ~ "A N",
                                 event_seq == "N" ~ "A N",
                                 event_seq == "! N Z" ~ "! A N Z",
                                 event_seq == "! L N" ~ "! A L N",
                                 TRUE ~ event_seq))
```

### Events

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}

CORE_EXPLICIT_ENV_EVENT_SEQ <-
    CORE_EXPLICIT_ENV %>%
    group_by(event_seq) %>%
    summarize(count = sum(count), sources = paste(unique(primary_source), collapse="|")) %>%
    ungroup() %>%
    arrange(desc(count)) %>%
    mutate(cumperc = round(100 * cumsum(count)/ sum(count), 2))

datatable(CORE_EXPLICIT_ENV_EVENT_SEQ)

CORE_EXPLICIT_ENV_EVENT_SEQ %>%
mutate(count = label_number_si(0.1)(count)) %>%
slice(1:20) %>%
pmap_chr(function(event_seq, count, sources, cumperc) {
    sprintf("\\texttt{%s}&%s&%.1f\\%%", event_seq, count, cumperc)
}) %>%
as_tex_table()

cat("Total Core environments: ", sum(CORE_EXPLICIT_ENV_EVENT_SEQ$count))
```

### Packages

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
CORE_EXPLICIT_ENV_PACKAGES  <-
    CORE_EXPLICIT_ENV %>%
    count(package, wt = count, name = "count") %>%
    arrange(desc(count)) %>%
    mutate(cumperc = round(100 * cumsum(count)/ sum(count), 2)) %>%
    mutate(count = label_number_si(0.1)(count))

datatable(CORE_EXPLICIT_ENV_PACKAGES)

CORE_EXPLICIT_ENV_PACKAGES %>%
slice(1:14) %>%
pmap_chr(function(package, count, cumperc) {
    sprintf("\\code{%s}&%s&%.1f\\%%", package, count, cumperc)
}) %>%
as_tex_table()

cat("Total Explicit Core Packages: ", nrow(CORE_EXPLICIT_ENV_PACKAGES))
```

### Functions

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
CORE_EXPLICIT_ENV_FUNCTIONS <-
    CORE_EXPLICIT_ENV %>%
    count(primary_source, wt = count, name = "count") %>%
    arrange(desc(count)) %>%
    mutate(cumperc = round(100 * cumsum(count)/ sum(count), 2)) %>%
    mutate(count = label_number_si(0.1)(count))

datatable(CORE_EXPLICIT_ENV_FUNCTIONS)

CORE_EXPLICIT_ENV_FUNCTIONS %>%
slice(1:10) %>%
pmap_chr(function(primary_source, count, cumperc) {
    fun <- str_replace_all(primary_source, fixed("*$#$*"), "::")
    sprintf("\\code{%s}&%s&%.1f\\%%", fun, count, cumperc)
}) %>%
as_tex_table()

cat("Total Explicit Core Functions: ", nrow(CORE_EXPLICIT_ENV_FUNCTIONS))
```

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
CORE_EXPLICIT_ENV_CLASS <-
    CORE_EXPLICIT_ENV %>%
    filter(!is.na(class)) %>%
    mutate(kind = case_when(str_ends(class, fixed("ggproto|gg")) ~ "ggplot2::ggproto|gg",
                            str_ends(class, fixed("replot_xts|environment")) ~ "xts::replot_xts|environment",
                            str_ends(class, fixed("XMLHashTree|XMLAbstractDocument")) ~ "XML::XMLHashTree|XMLAbstractDocument",
                            str_ends(class, fixed("event_loop")) ~ "later::event_loop",
                            str_ends(class, fixed("rlang_ctxt_pronoun")) ~ "rlang::rlang_ctxt_pronoun",
                            str_ends(class, fixed("r6lite")) ~ "rlang::r6lite",
                            str_ends(class, fixed("idf|environment")) ~ "plyr::idf|environment",
                            class == "R6ClassGenerator" ~ "R6::R6ClassGenerator",
                            str_detect(class, fixed("session_proxy")) ~ "shiny::session_proxy",
                            str_detect(class, fixed("R6")) ~ "R6::R6",
                            TRUE ~ NA_character_)) %>%
    filter(!is.na(kind)) %>%
    count(kind, wt = count, name = "count") %>%
    arrange(desc(count)) %>%
    mutate(cumperc = round(100 * cumsum(count)/ sum(count), 2))

CORE_EXPLICIT_ENV_CLASS %>%
mutate(count = label_number_si(0.1)(count)) %>%
datatable()

CORE_EXPLICIT_ENV_CLASS %>%
mutate(count = label_number_si(0.1)(count)) %>%
pmap_chr(function(kind, count, cumperc) {
    splits <- str_split(kind, fixed("::"))[[1]] 
    package <- splits[1]
    classes <- splits[2]
    classes <- str_replace_all(classes, fixed("|"), " ")
    sprintf("\\texttt{%s}&\\texttt{%s}&%s&%.1f\\%%", package, classes, count, cumperc)
}) %>%
as_tex_table()

cat("Total environments with attributes: ", sum(CORE_EXPLICIT_ENV_CLASS$count))
cat("% environments with attributes: ", sum(CORE_EXPLICIT_ENV_CLASS$count) / sum(CORE_EXPLICIT_ENV_EVENT_SEQ$count))
```


## Call Environments

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}

CALL_ENV <-
    all_env %>%
    filter(category == "Call") %>%
    process_event_seq() %>%
    mutate(event_seq = case_when(event_seq == "X" | event_seq == "A X" ~ "A X",
                                 event_seq == "V X" | event_seq == "A V X" | event_seq == "U X" ~ "A V X",
                                 event_seq == "S V X" | event_seq == "A S V X" ~ "A S V X",
                                 event_seq == "# A" | event_seq == "# X" ~ "# A X",
                                 event_seq == "A" ~ "",
                                 event_seq == "! A V X" | event_seq == "! V X" ~ "! A V X",
                                 event_seq == "A V" | event_seq == "V" ~ "A V",
    ##       event_seq == "E+ [ A+ ]+" | event_seq == "E+ [ A+ ]+ S+" | event_seq == "E+ { }" | event_seq == "S+ E+ [ A+ ]+ { A+ } E+" | event_seq == "E+ [ A+ ]+ E+ [ A+ ]+" | event_seq == "E+ [ A+ ]+ E+" | event_seq == "E+ [ A+ ]+ E+ [ A+ ]+ S+" ~ "S* E* [ A* ]+ E* S*",
    ##        event_seq == "E+ # [ A+ ]+" | event_seq == "E+ [ A+ ]+ # [ A+ ]+" ~ "E+ [ A+ ]* # [ A+ ]+",
                                 TRUE ~ event_seq))
CALL_ENV_EVENT_SEQ <-
    CALL_ENV %>%
    group_by(event_seq) %>%
    summarize(count = sum(count)) %>%
    ungroup() %>%
    mutate(escaped = str_detect(event_seq, fixed("#")))
    
cat("Total calls: ", sum(CALL_ENV$count))
```

### Normal Calls

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
NORMAL_CALL_ENV_EVENT_SEQ <-
    CALL_ENV_EVENT_SEQ %>%
    filter(!escaped) %>%
    filter(event_seq != "") %>%
    arrange(desc(count)) %>%
    mutate(cumperc = round(100 * cumsum(count)/ sum(count), 2))

datatable(NORMAL_CALL_ENV_EVENT_SEQ)

NORMAL_CALL_ENV_EVENT_SEQ %>%
mutate(count = label_number_si(0.1)(count)) %>%
slice(1:4) %>%
pmap_chr(function(event_seq, count, escaped, cumperc) {
    sprintf("\\texttt{%s}&%s&%.1f\\%%", event_seq, count, cumperc)
}) %>%
as_tex_table()

cat("Normal calls: ", sum(NORMAL_CALL_ENV_EVENT_SEQ$count))
cat("Useless calls: ", sum(CALL_ENV$count) - sum(NORMAL_CALL_ENV_EVENT_SEQ$count))
```

### Escaped Calls

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}

ESCAPED_CALL_ENV_EVENT_SEQ <-
    CALL_ENV_EVENT_SEQ %>%
    filter(escaped) %>%
    arrange(desc(count)) %>%
    mutate(cumperc = round(100 * cumsum(count)/ sum(count), 2))

datatable(ESCAPED_CALL_ENV_EVENT_SEQ)

ESCAPED_CALL_ENV_EVENT_SEQ %>%
mutate(count = label_number_si(0.1)(count)) %>%
slice(1:4) %>%
pmap_chr(function(event_seq, count, escaped, cumperc) {
    sprintf("\\texttt{%s}&%s&%.1f\\%%", event_seq, count, cumperc)
}) %>%
as_tex_table()

cat("Escaped calls: ", sum(ESCAPED_CALL_ENV_EVENT_SEQ$count))
```

### Qualitative Examples

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
CALL_ENV %>%
    filter(event_seq == "S") %>%
    count(orig_fun_name, wt = count, name = "count") %>%
    arrange(desc(count)) %>%
    mutate(cumperc = round(100 * cumsum(count)/ sum(count), 2)) %>%
    mutate(count = label_number_si(0.1)(count)) %>%
    slice(1:100) %>%
    datatable()
    
    
CALL_ENV %>%
    filter(event_seq == "A X") %>%
    count(orig_fun_name, wt = count, name = "count") %>%
    arrange(desc(count)) %>%
    mutate(cumperc = round(100 * cumsum(count)/ sum(count), 2)) %>%
    mutate(count = label_number_si(0.1)(count)) %>%
    slice(1:100) %>%
    datatable()

CALL_ENV %>%
    filter(event_seq == "A V X") %>%
    count(orig_fun_name, source_fun_name_1, source_fun_name_2, wt = count, name = "count") %>%
    arrange(desc(count)) %>%
    mutate(cumperc = round(100 * cumsum(count)/ sum(count), 2)) %>%
    mutate(count = label_number_si(0.1)(count)) %>%
    slice(1:100) %>%
    datatable()

CALL_ENV %>%
    filter(event_seq == "A S V X") %>%
    count(orig_fun_name, wt = count, name = "count") %>%
    arrange(desc(count)) %>%
    mutate(cumperc = round(100 * cumsum(count)/ sum(count), 2)) %>%
    mutate(count = label_number_si(0.1)(count)) %>%
    slice(1:100) %>%
    datatable()
    
CALL_ENV %>%
    filter(event_seq == "S X") %>%
    count(orig_fun_name, wt = count, name = "count") %>%
    arrange(desc(count)) %>%
    mutate(cumperc = round(100 * cumsum(count)/ sum(count), 2)) %>%
    mutate(count = label_number_si(0.1)(count)) %>%
    slice(1:100) %>%
    datatable()    

##    all_env %>%
##    filter(category == "Call") %>%
##    process_call_event_seq() %>%
##    filter(event_seq == "|parent.frame_0|") %>%
##    arrange(desc(count)) %>%
##    mutate(cumperc = round(100 * cumsum(count)/ sum(count), 2)) %>%
##    mutate(count = label_number_si(0.1)(count)) %>%
##    slice(1:100) %>%
##    datatable()
```
