---
title: "Corpus"
output:
    html_document:
        toc: true
        toc_depth: 3
        toc_float: true
        number_sections: true
        theme: cerulean
        highlight: pygments
        code_folding: hide
        fig_width: 9
        fig_height: 3
        css: style.css
params:
    datadir: "./data"
    graphdir: "./graphs"
    macrodir: "./macros"
    tabledir: "./tables"
---

```{r echo = FALSE, warning=FALSE, message=FALSE}
## https://bookdown.org/yihui/rmarkdown-cookbook/source-script.html
source("analysis.R", local = knitr::knit_global())
MacGen <- LatexMacroGenerator$new(params$macrodir)

PACKAGE_INFO <-
    package_info %>%
    select(package, funname, param_count = arity) %>%
    mutate(funname = paste0("`", funname, "`"))
```

## Corpus

### Number of packages

There are `r length(corpus)` packages selected for the corpus. They have `r length(client)` 
dependents. These in-turn invoke functions from other packages.
The table below shows the packages directly selected as part of the corpus and
the packages invoked transitively.

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
corpus_extra <-
    functions %>%
    filter(pack_name != "<NA>") %>%
    pull(pack_name) %>%
    unique() %>%
    setdiff(corpus) %>%
    setdiff(c("base", "compiler", "datasets", "grDevices",
              "graphics", "grid", "methods", "parallel",
              "profile", "splines", "stats", "stats4",
              "tcltk", "tools", "translations", "utils"))
    
corpus_table <-
tibble(package = corpus, type = "direct") %>%
bind_rows(tibble(package = corpus_extra, type = "indirect"))

datatable(corpus_table)

PACKAGE_NAMES <- corpus_table$package
```

There are `r length(corpus_extra)` transitively selected packages.


## Number of dependencies

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
client_counts <-
    package_table %>%
    group_by(package) %>%
    summarize(client_count = length(unique(client))) %>%
    ungroup()
    
corpus_table %>%
left_join(client_counts, by = "package") %>%
datatable()
```
# Package Code

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
summarize_sloc <- function(df, packages, types = c("test", "example", "testthat", "vignette")) {
    df %>%
        filter(package %in% packages) %>%
        filter(type %in% types) %>%
        filter(language %in% c("R", "C/C++ Header", "C", "C++", "Fortran 77")) %>%
        mutate(language = case_when(language == "R" ~ "R", TRUE ~ "Native")) %>%
        group_by(language, type) %>%
        summarize(count = n(), code = sum(code)) %>%
        ungroup()
}
```

The table below shows the amount of code in the corpus packages.

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
direct_package_code <- summarize_sloc(sloc_package,
                                      corpus_table$package[corpus_table$type == "direct"], c("R", "src"))

indirect_package_code <- summarize_sloc(sloc_package, 
                                        corpus_table$package[corpus_table$type == "indirect"], c("R", "src"))

package_code <- 
    add_column(direct_package_code, kind = "direct", .before = 1) %>%
    bind_rows(add_column(indirect_package_code, kind = "indirect", .before = 1)) %>%
    group_by(kind, language) %>%
    summarize(count = sum(count), code = sum(code)) %>%
    ungroup() %>%
    mutate(count = label_number_si(accuracy = 0.1)(count),
           code = label_number_si(accuracy = 0.1)(code))

package_code %>% show_table()
```

# Script Code

The table below shows the amount of code in the scripts used for evaluation.

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
runnable_code <-
    sloc_script %>%
    mutate(type = case_when(type == "testthat" ~ "test",
                            TRUE ~ type)) %>%
    summarize_sloc(corpus) %>%
    mutate(count = label_number_si(accuracy = 0.1)(count),
           code = label_number_si(accuracy = 0.1)(code))

runnable_code %>% show_table()
```

# Package Functions
```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
fun_dist <-
    functions %>% 
    filter(outer, !anonymous, pack_name %in% PACKAGE_NAMES) %>%
    count(pack_name, fun_name, wt = call_count, name = "call_count")

cat("Total exercised functions: ", nrow(fun_dist))

fun_dist %>%
    count(pack_name, name = "function_count") %>%
    arrange(desc(function_count)) %>%
    datatable()

fun_dist <-
    fun_dist %>%
    count(pack_name, name = "count") %>%
    mutate(min_range = floor(count/25),
           max_range = ceiling(count/25)) %>%
    mutate(min_range = if_else(min_range == max_range, min_range - 1, min_range)) %>%
    mutate(functions = paste0(min_range * 25 + 1, " - ", max_range * 25)) %>% 
    count(min_range, functions, name = "packages") %>%
    arrange(min_range) %>%
    select(functions, packages)

fun_dist %>% datatable()
```
# Calls

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}

call_dist <-
    functions %>% 
    filter(outer, !anonymous, pack_name %in% PACKAGE_NAMES) %>%
    group_by(pack_name, fun_name) %>%
    summarize(call_count = first(call_count)) %>%
    ungroup()


called_never_funs <-
    PACKAGE_INFO %>%
    filter(package %in% PACKAGE_NAMES) %>%
    left_join(call_dist, by = c("package" = "pack_name", "funname" = "fun_name")) %>%
    select(pack_name = package, fun_name = funname, call_count) %>%
    mutate(call_count = if_else(is.na(call_count), 0L, call_count)) %>%
    filter(call_count == 0)
    
cat("Never called functions:", nrow(called_never_funs))
cat("Never called packages:", length(unique(called_never_funs$pack_name)))

called_never_packs <-
    called_never_funs %>%
    count(pack_name, name = "fun_count") %>%
    left_join(corpus_table, by = c("pack_name" = "package")) %>%
    group_by(type) %>%
    summarize(pack_count = n(), fun_count = sum(fun_count))
    
datatable(called_never_packs)

called_once_packs <-
    call_dist %>%
    filter(call_count == 1) %>%
    pull(pack_name) %>%
    unique() %>%
    length()
    
cat("Total number of calls:", sum(call_dist$call_count))
cat("Packages whose functions are called only once:", called_once_packs)
    
call_dist <-
    call_dist %>%
    mutate(call_count = if_else(call_count <= 10, as.character(call_count), "> 10")) %>%
    count(call_count, name = "fun_count") %>%
    mutate(relative_fun_count = fun_count/sum(fun_count)) %>%
    arrange(desc(fun_count)) %>%
    mutate(cumperc = round(100 * cumsum(fun_count) / sum(fun_count), 2))
            
datatable(call_dist)

total_function_count <- sum(call_dist$fun_count)

call_dist_plot <-
    call_dist %>%
    ggplot(aes(call_count, relative_fun_count)) + 
    geom_col(fill = "black") +
    scale_y_continuous(sec.axis = sec_axis(~ . * total_function_count,
                                           labels = label_number_si()),
                       labels = label_percent()) +
    scale_x_discrete(limits = c(1:10, "> 10")) +
    coord_flip()+
    labs(x = "Calls", y = "Functions")

save_as_tikz(call_dist_plot, "call_dist")
```

# Parameters

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
param_dist <-
    functions %>% 
    filter(outer, !anonymous, pack_name %in% PACKAGE_NAMES) %>%
    distinct(pack_name, fun_name) %>%
    left_join(PACKAGE_INFO, by = c("pack_name" = "package", "fun_name" = "funname")) %>%
    select(pack_name, fun_name, param_count) %>%
    mutate(param_count = if_else(is.na(param_count), 0L, param_count))
    
datatable(param_dist)

    
param_dist %>%
filter(param_count > 50) %>%
select(pack_name, fun_name, param_count) %>%
pmap_chr(function(pack_name, fun_name, param_count) paste0(pack_name, "::", fun_name, "->", param_count)) %>%
print()

param_dist <-
    param_dist %>%
    count(param_count, name = "fun_count") %>%
    arrange(desc(fun_count)) %>%
    mutate(cumperc = round(100 * cumsum(fun_count) / sum(fun_count), 2))
    
datatable(param_dist)

cat("Total parameter positions: ", sum(param_dist$param_count * param_dist$fun_count), "\n")

total_function_count <- sum(param_dist$fun_count)

param_dist <-
    param_dist %>%
    mutate(param_count = if_else(param_count <= 10, as.character(param_count), "> 10")) %>%
    count(param_count, wt = fun_count, name = "fun_count") %>%
    mutate(relative_fun_count = fun_count/sum(fun_count))
    
datatable(param_dist)

param_dist_plot <-
    ggplot(param_dist, aes(param_count, relative_fun_count)) + 
    geom_col(fill = "black") +
    scale_y_continuous(sec.axis = sec_axis(~ . * total_function_count,
                                           labels = label_number_si()),
                       labels = label_percent()) +
    scale_x_discrete(limits = c(0:10, "> 10")) +
    coord_flip()+
    labs(x = "Parameters", y = "Functions")

save_as_tikz(param_dist_plot, "param_dist")
```
