---
title: "new.env"
output:
    html_document:
        toc: true
        toc_depth: 3
        toc_float: true
        number_sections: true
        theme: cerulean
        highlight: pygments
        code_folding: hide
        fig_width: 9
        fig_height: 3
        css: style.css
params:
    datadir: "./data"
    graphdir: "./graphs"
    macrodir: "./macros"
    tabledir: "./tables"
---

```{r echo = FALSE, warning=FALSE, message=FALSE}
## https://bookdown.org/yihui/rmarkdown-cookbook/source-script.html
source("analysis.R", local = knitr::knit_global())
```

# new.env Caller Proportion

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
env_cons %>%
    count(source_fun_name_1, source_fun_name_2, source_fun_name_3, source_fun_name_4, 
    wt = count, name = "count") %>%
    arrange(desc(count)) %>%
    datatable()

env_cons %>%
    count(source_fun_name_1, wt = count, name = "count") %>%
    arrange(desc(count)) %>%
    datatable()
    
env_cons %>%
    count(source_fun_name_2, wt = count, name = "count") %>%
    arrange(desc(count)) %>%
    datatable()
    
env_cons %>%
    count(source_fun_name_3, wt = count, name = "count") %>%
    arrange(desc(count)) %>%
    datatable()
    
env_cons %>%
    count(source_fun_name_4, wt = count, name = "count") %>%
    arrange(desc(count)) %>%
    datatable()
```

# new.env classification

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
env_cons <-
    env_cons %>%
    mutate(primary_source = case_when(str_starts(source_fun_name_1, fixed("base*$#$*lazyLoadDBexec")) ~ source_fun_name_1,
                                      str_starts(source_fun_name_2, fixed("base*$#$*lazyLoadDBexec")) ~ source_fun_name_2,
                                      str_starts(source_fun_name_2, fixed("base*$#$*loadNamespace")) ~ source_fun_name_2,
                                      source_fun_name_1 == "base*$#$*new.env" & is.na(source_fun_name_2) ~ "base*$#$*package_load_file",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*5d8ec22f1fac51fafcb0a876cc9a1dad489c1b41bfc4427f6634a9857d6e45a22b0c5a8504ee92c76d994698a2b00900888d4df7fa22d64c4e0196443f11c9b2" ~ "dplyr*$#$*dplyr_lazy_vec_chop_impl",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*24a2bd9ef1d1d0bed806a984c395ea21bbe8f6c7e28034d5ab619490dfd2057496cb2893ea5f506ca61e31d3580e8e2ed220a9fc53ee5970cabc102f8fd241eb" ~ "R6*$#$*R6Class",
                                      
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*2ae04899b56d2a4922d9088b16dca9f5493c3ceb37dabbfb0d6625d23af95e73e9e212ac86b83f1445eacfdbd3fa81b3a661bb7f3c5da3fa04debfa085395681*$#$*make_first_new_slice" ~ "R6*$#$*make_first_new_slice",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*2ae04899b56d2a4922d9088b16dca9f5493c3ceb37dabbfb0d6625d23af95e73e9e212ac86b83f1445eacfdbd3fa81b3a661bb7f3c5da3fa04debfa085395681*$#$*make_new_slice" ~ "R6*$#$*make_new_slice",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*clone*$#$*make_new_slice" ~ "R6*$#$*make_new_slice",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*copy" ~ "lme4*$#$*merPredD*$#$*copy",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*829b877f5e7b68192afbd9af2c4c159e08a96ffb2169b846ab54cec6eab9b2122aee15552088cfbb79051662709544dd40cc1a037b3da266a43d372317870ab9" ~ "shiny*$#$*RestoreContext*$#$*reset",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*checkMatrix" ~ "Matrix*$#$*checkMatrix",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*new" ~ "R6*$#$*generator_funs*$#$*new",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*create_super_env" ~ "R6*$#$*create_super_env",
                                      
                                      
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*clone*$#$*make_first_new_slice" ~ "R6*$#$*make_first_new_slice",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*initialize" ~ "R6*$#$*generator_funs*$#$*new",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*271ae2fa8d46b84c79a0b568c8ce6fb89fe66b0ad80a18be62ae15dcf13a1fd0701aaf43706e7c4bd694aa4f34c809f2551e010abff6210ed4fe8a8c3ac7980f" ~ "httpuv*$#$*AppWrapper*$#$*initialize",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*cad9f5e72cf80a892ad8cee6ac96c942739dbf25a9e519a0dbe833aaab59778cf815f838583bf8fb528a743bff410b0e1db9bfa2597a1d046c11111e2a1fcd70" ~ "methods*$#$*.InitMethodDefinitions*$#$*initialize",                                  
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*53f26b2cc4bd7c82af8e9821b32aefa979dab81840aaac8996db5353037c0ddc5f41064696a9181d13d0362cc7c6d3deed1fcc3da364a0db446ab271b90e4f08" ~ "shiny*$#$*shinyAppDir_serveR",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*moreSessionInfo" ~ "CLA*$#$*moreSessionInfo",
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*5ee24a437c49708a0c574d944232c19f979e7bc53cbdeac097f0155a96b32aa49322aad1e26a9df50e9e9f3230a5b20f95616d31116f1e010eec4d1b9594a97a" ~ "dplyr*$#$*tests*$#$*testthat*$#$*test-across.R",                     
                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*5ee24a437c49708a0c574d944232c19f979e7bc53cbdeac097f0155a96b32aa49322aad1e26a9df50e9e9f3230a5b20f95616d31116f1e010eec4d1b9594a97a" ~ "dplyr*$#$*tests*$#$*testthat*$#$*test-across.R",                        source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*c2fc402d1f015684f414ec363dfa3b4f339189c31f973af868049d096b5b1ac3d14ea80c1b6c7e00f1e90e533871e10dfefdf9f5c2c83303c17e6feb077bf8e5" ~ "R6*$#$*examples*$#$*CustomCloner",                                      source_fun_name_1 == "base*$#$*new.env" & source_fun_name_2 == "<NA>*$#$*r_parse_eval" ~ "rlang*$#$*tests*$#$*testthat*$#$*helper-c-api.R",                    
                                      TRUE ~ source_fun_name_2)) %>%
    mutate(package = map_chr(str_split(primary_source, fixed("*$#$*")), ~.[1]))
    
    move nlme to base, it uses local function.

datatable(env_cons)
    
env_cons_by_package <-
    env_cons %>%
    filter(!(package %in% c("base", "methods", "compiler", "stats"))) %>%
    count(package, wt = count, name = "count") %>%
    arrange(desc(count)) %>%
    mutate(cumperc = round(100 * cumsum(count)/ sum(count), 2))
    
datatable(env_cons_by_package)

print(env_cons_by_package)


env_cons_by_package_and_function <-
    env_cons %>%
    filter(!(package %in% c("base", "methods", "compiler"))) %>%
    count(package, primary_source, wt = count, name = "count") %>%
    arrange(desc(count)) %>%
    mutate(cumperc = round(100 * cumsum(count)/ sum(count), 2))

datatable(env_cons_by_package_and_function)
```

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
env_cons %>% 
    mutate(pack = case_when(str_starts(source_fun_name_1, "$<NA>*$#$*") ~ "NA",
                            TRUE ~ str_extract(source_fun_name_1, "$.*[*][$][#][$][*].*"))) %>%
    count(pack, wt = count, name = "count") %>%
    arrange(desc(count)) %>%
    mutate(cp = cumsum(count)/sum(count))
``

### codetools
#### mkHash
https://github.com/cran/codetools/blob/master/R/codetools.R#L17
Creates an environment to use as a hash table, so the parent is empty.
The package is geared towards analysis of R code for byte-code compilation.
It uses uses hash tables to store intermediate static analysis information.

#### collectUsageFun
https://github.com/cran/codetools/blob/master/R/codetools.R#L457
this uses new.env as part of the analysis state to extend the lexical scope of a
function before analyzing it and seeds it with the all the parameter and local
variables of the function. This gives it access

### ggplot2
#### ggproto
https://github.com/tidyverse/ggplot2/blob/master/R/ggproto.r#L58
Used by the venerable ggplot2 library to create a prototype based OO system. All its objects are represented using ggproto. the
object is reprsented by an environment with empty parent.
Copies provided members to environment using list2env, attaches a superclass if provided, sets class attributes and returns.
```
class(e) <- c(`_class`, class(super))
or
class(e) <- c(`_class`, "ggproto", "gg")
```

### grid
#### pushedvp
https://github.com/thomasp85/grid/blob/1cf78ea669c93e8b870c2df3156e8785547ebbc1/R/viewport.R#L115
creates a new viewport and stores the children in a hash table with viewport names as keys.


### testthat
#### describe
This function implements a simple BDD DSL for writing tests, inspired by
     RSpec for Ruby or Mocha for JavaScript.
describe("math library", {
       describe("addition()", {
         it("can add two numbers", {
           expect_equal(1 + 1, addition(1, 1))
         })
       })
The describe function creates a new environment and evaluates the testing code block in it to contain side effects.
The new environment uses the caller's enviornment as its parent to look up the free variables of the code block.
#### test_code
test_code is an internal function used by testing wrappers. It takes a block of
code for testing and evaluates it in a custom environment constructed with a
parent enviroment passed as argument. In fact, describe function internally uses test_code.


### forecast
The R package forecast provides methods and tools for displaying and analysing univariate time series forecasts i
Does Uses new.env in 2 places to store model/function options.

### data.table
#### frollapply
This function computes rolling aggregate using a user-supplied function.
For performance, the kernel is implemented in C. It repeatedly calls the function with the next window and arbitrary varargs.
This evaluation is performed in a new environment which extens the frollapply call environment to enable the access of varaargs.


#### [.data.table
This function uses new.env three times. It implements subsetting semantics for data.table which is a DSL for data frame. The environments inherit from caller environment and are extended with custom variables for evalutaion to implement the DSL.

#### test.data.table
This function uses new.env for testing, extending it with globalenv. It adds fields to keep track of number of executed and failed tests and also evaluates the test code in this environment.


### R.oo

#### Object
Creates a new environment, attaches it as an attribute to the object being constructed for storing its fields.

#### clone.Object
Clones the object, creates a new environment, to store the attributes of the cloned object

#### .subset2Internal.Class

Allows access to object fields via [[ and $ operators of R.
When accessing static methods, it 
      code <- sprintf("function(...) \"%s\"(static, ...)", name)
      expr <- base::parse(text=code)
      fcn <- eval(expr)

      # Set the environment of the static function to inherit from the
      # environment of the static instance/object, which in turn is the
      # same as the environment of the Class/constructor.
      envT <- environment(static)

      # BACKWARD COMPATIBILTY/ROBUSTNESS: In case an old static object
      # has been loaded, make sure to not crash, i.e. behave as before.
      if (!is.null(envT)) {
        env <- new.env(parent=envT)
        env$static <- static
        environment(fcn) <- env
      }

### foreach

#### foreach and xforeach
They create an environment each with empty env as parent for storing the dynamic state of the iterator.

#### doSEQ and %do%
Create environment to evaluate the expression.
Another one creates an extra environment in the chain to attach a value to signal the function where it is called from.


### iterators
#### iter.default and iter.matrix and iter.data.frame and iter.function
Create environment to store iterator state (object and index) updated during traversal.

### later
#### create_loop + .globals + .loops
Uses new environment to represent event_loop objects to schedule and execute functions.
Creates a .globals new environment that stores a reference to global event loop objects and a .loops environment to store private event loops

### xts
#### merge.xts
Creates a new environment which inherits the caller's environment, passed to native code to evaluate expressions which reference pakcage functions.
#### new.replot_xts and new.replot_xts*$#$*3f5de24fbfe2cab73d76b0c5e766203348ba70cd0af2bb2041ff6d2001f5abac588582dad3c611024aaa3323826ec4e0bea0c63093f51fe0d6dd4f3aba30e0ef
Creates environments to represent plotting objects containing axes limits and padding information.
Also attaches methods to the environment that update this information.
Attaches new_environment function which inherits from the parent environment to create a new plotting environment.
#### as.environment.xts
Overloads as.environment to xts objects to copy their data to a new environment. xts objects are extensible 
time-series objects.

### Rcpp
Creates .classes_map environment at pakcag level as a hash table mapping typeid to Class objects.
Creates a new.env as a hash map to key objects against their demangled names.


#### 



Classification by source
- implementation (R + C) [ new.env + allocSExp + NewEnvironment HashedEnvironment ]
- packages (R + C) [ new.env + allocSExp ]

Classification by use?
- call
- package
- S4
- native code
- eval
- metaprogramming
- formulas
- package state
- object-oriented system
- env to list and list to env

