---
title: "Scope"
output:
    html_document:
        toc: true
        toc_depth: 3
        toc_float: true
        number_sections: true
        theme: cerulean
        highlight: pygments
        code_folding: hide
        fig_width: 9
        fig_height: 3
        css: style.css
params:
    datadir: "./data"
    graphdir: "./graphs"
    macrodir: "./macros"
    tabledir: "./tables"
---

```{r echo = FALSE, warning=FALSE, message=FALSE}
## https://bookdown.org/yihui/rmarkdown-cookbook/source-script.html
source("analysis.R", local = knitr::knit_global())
MacGen <- LatexMacroGenerator$new(params$macrodir)
```

## Table Structure


```{r, eval = TRUE}
str(call_stack)
```


## All functions

```{r, eval = TRUE}
call_stack %>% 
count(fun_name, wt = count, name = "count") %>%
arrange(desc(count))
```


# environment

## Raw

```{r, eval = TRUE}
ENVIRONMENT_TABLE <-
    call_stack %>%
    filter(fun_name == "environment") %>%
    filter(!is.na(fun_qual_name)) %>%
    mutate(aliased = qual_name_1 != "base*$#$*environment") %>%
    mutate(source = paste0(package, "*$#$*", type, "/", filename)) %>%
    mutate(qual_name_2 = case_when(str_starts(call_expr, fixed("environment(plot_snapshot)")) ~ "evaluate*$#$*evaluate",
                                   qual_name_2 == "<NA>*$#$*2ae04899b56d2a4922d9088b16dca9f5493c3ceb37dabbfb0d6625d23af95e73e9e212ac86b83f1445eacfdbd3fa81b3a661bb7f3c5da3fa04debfa085395681*$#$*remap_func_envs*$#$*655729dd5ad88c8d804343ea7f72e9e0e26fe2b9781998c9a0df54061a1a818cdcddffdc3f868a18f3559ea5c228b7773a58b4c6cabf8b5f0a73a540337960a7" ~ "generator_funs*$#$*clone_method*$#$*copy_slice*$#$*is_method",
                                   qual_name_2 == "<NA>*$#$*2ae04899b56d2a4922d9088b16dca9f5493c3ceb37dabbfb0d6625d23af95e73e9e212ac86b83f1445eacfdbd3fa81b3a661bb7f3c5da3fa04debfa085395681*$#$*copy_slice*$#$*is_method" ~ "generator_funs*$#$*clone_method*$#$*copy_slice*$#$*is_method",
                                   qual_name_2 == "<NA>*$#$*getSpline.xy" ~ paste0("robustbase*$#$*", source, "/getSpline.xy"),
                                   qual_name_2 == "<NA>*$#$*rewire" ~ paste0("shiny*$#$*", source, "/rewire"),
                                   TRUE ~ qual_name_2)) %>%
    mutate(pack_name = map_chr(str_split(qual_name_2, fixed("*$#$*")), ~.[1])) %>%
    mutate(result_pack_name = map_chr(str_split(result_env_qual_name, fixed("*$#$*")), ~.[1])) %>%
    mutate(category = case_when(str_detect(qual_name_2, fixed("/")) ~ "Top-Level",
                                pack_name %in% CORE_PACKAGES ~ "Core",
                                TRUE ~ "User")) %>%
    count(fun_name, n, source, call_expr, aliased, category, pack_name, qual_name_2, qual_name_3, qual_name_4, fun_qual_name, result_pack_name, result_env_qual_name, wt = count, name = "calls") %>%
    arrange(desc(calls))
    
datatable(ENVIRONMENT_TABLE)
```

## Top Callers

```{r, eval = TRUE}
ENVIRONMENT_TABLE %>%
    count(qual_name_2, wt = calls, name = "calls") %>%
    arrange(desc(calls)) %>%
    mutate(call_perc = round(100 * calls / sum(calls), 2)) %>%
    mutate(call_cumperc = round(100 * cumsum(calls) / sum(calls), 2)) %>%
    datatable()
```

## Cleanup

```{r, eval = TRUE}
ENVIRONMENT_TABLE %>%
    mutate(type = str_starts(fun_qual_name, fixed("<NA>"))) %>%
    count(type, wt = calls, name = "calls") %>%
    datatable()

ENVIRONMENT_TABLE %>%
    count(fun_qual_name, wt=calls, name="calls") %>%
    filter(str_starts(fun_qual_name, fixed("<NA>"))) %>%
    arrange(desc(calls)) %>%
    datatable()


EnvironmentBaseRegisterMethodCallCount <- 
    ENVIRONMENT_TABLE %>%
    filter(str_starts(qual_name_2, fixed("base*$#$*registerS3methods"))) %>%
    pull(calls) %>%
    sum()
    
EnvironmentMethodsCallCount <- 
    ENVIRONMENT_TABLE %>%
    filter(str_starts(qual_name_2, fixed("methods*$#$*"))) %>%
    pull(calls) %>%
    sum()

EnvironmentBaseRegisterMethodCallPerc <- 
    latex_sanitize(label_percent(0.1)(EnvironmentBaseRegisterMethodCallCount / sum(ENVIRONMENT_TABLE$calls)))
    
EnvironmentMethodsCallPerc <- 
    latex_sanitize(label_percent(0.1)(EnvironmentMethodsCallCount / sum(ENVIRONMENT_TABLE$calls)))
    
MacGen$from_args(EnvironmentBaseRegisterMethodCallPerc = EnvironmentBaseRegisterMethodCallPerc)
MacGen$from_args(EnvironmentMethodsCallPerc = EnvironmentMethodsCallPerc)
```

## Summary

```{r, eval = TRUE}
ENVIRONMENT_TABLE %>%
    mutate(same_package = pack_name == result_pack_name) %>%
    group_by(category, same_package) %>%
    summarize(calls = sum(calls)) %>%
    ungroup() %>%
    mutate(call_perc = round(100 * calls / sum(calls), 2)) %>%
    datatable()

ENVIRONMENT_SUMMARY <-
    ENVIRONMENT_TABLE %>%
    group_by(fun_name, aliased, category) %>%
    summarize(calls = sum(calls),
              packages = length(unique(pack_name)),
              functions = length(unique(qual_name_2)),
              pack_names = paste(unique(pack_name), collapse = ", "),
              fun_names = paste(unique(qual_name_2), collapse = ", ")) %>%
    ungroup() %>%
    mutate(call_perc = round(100* calls / sum(calls), 2)) %>%
    arrange(desc(calls))

datatable(ENVIRONMENT_SUMMARY)

EnvironmentUnclassifiedCallCount <- 
    ENVIRONMENT_TABLE %>%
    filter(is.na(qual_name_2) | str_starts(qual_name_2, fixed("<NA>"))
           | qual_name_2 %in% c("base*$#$*lapply", "base*$#$*eval")) %>%
    pull(calls) %>%
    sum()

EnvironmentUnclassifiedCallPerc <- 
   latex_sanitize(label_percent(0.01)(EnvironmentUnclassifiedCallCount / sum(ENVIRONMENT_TABLE$calls)))

MacGen$from_args(EnvironmentUnclassifiedCallPerc = EnvironmentUnclassifiedCallPerc)

ENVIRONMENT_LATEX_TABLE <-
    ENVIRONMENT_TABLE %>%
    filter(!is.na(qual_name_2) & !str_starts(qual_name_2, fixed("<NA>"))) %>%
    filter(!(qual_name_2 %in% c("base*$#$*lapply", "base*$#$*eval"))) %>%
    filter(category != "Top-Level") %>%
    group_by(category) %>%
    summarize(CallCnt = sum(calls),
              PackCnt = length(unique(pack_name)),
              FunCnt = length(unique(qual_name_2)),
              pack_names = paste(unique(pack_name), collapse = ", "),
              fun_names = paste(unique(qual_name_2), collapse = ", ")) %>%
    ungroup() %>%
    mutate(CallPerc = latex_sanitize(label_percent()(round(CallCnt / sum(CallCnt), 2)))) %>%
    mutate(CallCnt = label_number_si(accuracy = 0.1)(CallCnt))
    
MacGen$from_df(ENVIRONMENT_LATEX_TABLE,
               PackCnt,
               FunCnt,
               CallCnt,
               CallPerc, 
               prefix = paste0("Environment", ENVIRONMENT_LATEX_TABLE$category))
```

# environment<-

## Raw

```{r, eval = TRUE}
ENVIRONMENT_ASSIGN_TABLE <-
    call_stack %>%
    filter(fun_name == "environment<-") %>%
    filter(!is.na(fun_qual_name)) %>%
    mutate(aliased = qual_name_1 != "base*$#$*environment<-") %>%
    mutate(source = paste0(package, "*$#$*", type, "/", filename)) %>%
    mutate(call_expr = str_trim(call_expr)) %>%
    mutate(qual_name_2 = case_when(qual_name_2 == "<NA>*$#$*d42bedd66f9bb747b3e3274ecc5e2225062540a513bec01f4f9049c536c209b6465f8a44c45cd24c760ec505cada18645411a3ac6693e3fc8afd42ddd6f071f9" ~ "methods*$#$*.makeDefaultBinding",
                                   qual_name_2 == "base*$#$*lapply" & qual_name_3 == "<NA>*$#$*assign_func_envs" ~ "R6*$#$*assign_func_envs",
                                   str_starts(call_expr, fixed("make.link(link")) ~ "stats*$#$*make.link",
                                   str_starts(call_expr, fixed("installClassMethod")) ~ "methods*$#$*installClassMethod",
                                   str_starts(call_expr, fixed("fix.family.link.family")) ~ "mgcv*$#$*fix.family.link.family",
                                   str_starts(call_expr, fixed("fix.family.var")) ~ "mgcv*$#$*fix.family.var",
                                   str_starts(call_expr, fixed("fix.family.ls")) ~ "mgcv*$#$*fix.family.ls",
                                   str_starts(call_expr, fixed("negative.binomial")) ~ "MASS*$#$*negative.binomial",
                                   str_starts(call_expr, fixed("rbdtree")) ~ "ape*$#$*rbdtree",
                                   str_starts(call_expr, fixed("mkdevfun")) ~ "lme4*$#$*mkdevfun",
                                   str_starts(call_expr, fixed("rpart")) ~ "rpart*$#$*rpart",
                                   str_starts(call_expr, fixed("psiFunc")) ~ "robustbase*$#$*psiFunc",
                                   str_starts(call_expr, fixed("set_env")) ~ "rlang*$#$*set_env",
                                   qual_name_2 == "R.oo*$#$*.subset2Internal" ~ "R.oo*$#$*.subset2Internal.Class",
                                   qual_name_2 == "base*$#$*mapply" & qual_name_3 == "shiny*$#$*addGeneratedInstanceMethods" ~ "shiny*$#$*addGeneratedInstanceMethods",
                                   str_starts(call_expr, fixed("fix.family.link.extended.family")) ~ "mgcv*$#$*fix.family.link.extended.family",
                                   str_starts(call_expr, fixed("foreach")) ~ "foreach*$#$*%do%",
                                   fun_qual_name == "lme4*$#$*mkLmerDevfun*$#$*devfun" ~ "lme4*$#$*mkLmerDevfun",
                                   str_starts(fun_qual_name, fixed("mgcv*$#$*ocat")) ~ "mgcv*$#$*ocat",
                                   str_starts(fun_qual_name, fixed("mgcv*$#$*scat")) ~ "mgcv*$#$*scat",
                                   str_starts(fun_qual_name, fixed("mgcv*$#$*negbin")) ~ "mgcv*$#$*negbin",
                                   str_starts(fun_qual_name, fixed("mgcv*$#$*tw")) ~ "mgcv*$#$*tw",
                                   str_starts(fun_qual_name, fixed("mgcv*$#$*twlss")) ~ "mgcv*$#$*twlss",
                                   str_starts(fun_qual_name, fixed("mgcv*$#$*ziP")) ~ "mgcv*$#$*ziP",
                                   str_starts(fun_qual_name, fixed("mgcv*$#$*betar")) ~ "mgcv*$#$*betar",
                                   str_starts(fun_qual_name, fixed("mgcv*$#$*cox.ph")) ~ "mgcv*$#$*cox.ph",
                                   str_starts(fun_qual_name, fixed("mgcv*$#$*nb")) ~ "mgcv*$#$*nb",
                                   str_starts(fun_qual_name, fixed("ape*$#$*rTraitMult")) ~ "ape*$#$*rTraitMult",
                                   str_starts(fun_qual_name, fixed("ape*$#$*rTraitCont")) ~ "ape*$#$*rTraitCont",
                                   str_starts(fun_qual_name, fixed("ape*$#$*rTraitDisc")) ~ "ape*$#$*rTraitDisc",
                                   str_starts(fun_qual_name, fixed("MASS*$#$*negative.binomial")) ~ "MASS*$#$*negative.binomial",
                                   fun_qual_name == "<NA>*$#$*d8bfb806e7653a6d3e3e27e652331fc534c0e62736ea1b66c8d6e544d4292c54608766e3039aadeb0c3b224324a52978cb3124377b4edb65f51120adfe81017c" ~ "foreach*$#$*%do%",
                                   str_starts(call_expr, fixed("idata.frame")) ~ "plyr*$#$*idata.frame",
                                   TRUE ~ qual_name_2)) %>%
    mutate(pack_name = map_chr(str_split(qual_name_2, fixed("*$#$*")), ~.[1])) %>%
    mutate(result_pack_name = map_chr(str_split(result_env_qual_name, fixed("*$#$*")), ~.[1])) %>%
    mutate(category = case_when(str_detect(qual_name_2, fixed("/")) ~ "Top-Level",
                                pack_name %in% CORE_PACKAGES ~ "Core",
                                TRUE ~ "User")) %>%
    count(fun_name, n, source, call_expr, aliased, category, pack_name, qual_name_2, qual_name_3, qual_name_4, fun_qual_name, result_pack_name, result_env_qual_name, wt = count, name = "calls") %>%
    arrange(desc(calls))
    
datatable(ENVIRONMENT_ASSIGN_TABLE)
```

## Top Callers

```{r, eval = TRUE}
ENVIRONMENT_ASSIGN_TOP_CALLERS <-
    ENVIRONMENT_ASSIGN_TABLE %>%
    count(qual_name_2, wt = calls, name = "calls") %>%
    arrange(desc(calls)) %>%
    mutate(call_perc = round(100 * calls / sum(calls), 2)) %>%
    mutate(call_cumperc = round(100 * cumsum(calls) / sum(calls), 2))
    
datatable(ENVIRONMENT_ASSIGN_TOP_CALLERS)

ENVIRONMENT_ASSIGN_TOP_CALLERS_LATEX <-
ENVIRONMENT_ASSIGN_TOP_CALLERS %>%
slice(1:5) %>%
rename(CallerName = qual_name_2, CallPerc = call_perc) %>%
mutate(CallerName = str_replace_all(CallerName, fixed("*$#$*"), "::")) %>%
mutate(CallerName = paste0("\\c{", latex_sanitize(CallerName), "}")) %>%
mutate(Position = c("One", "Two", "Three", "Four", "Five")) %>%
mutate(CallCount = label_number_si(accuracy = 0.1)(CallPerc / 100)) %>%
mutate(CallPercRaw = CallPerc) %>%
mutate(CallPerc = latex_sanitize(label_percent(0.1)(CallPerc / 100)))

ENVIRONMENT_ASSIGN_TOP_CALLERS_LATEX %>%
MacGen$from_df(CallerName,
               CallPerc,
               prefix = paste0("EnvAsn", ENVIRONMENT_ASSIGN_TOP_CALLERS_LATEX$Position))
               
MacGen$from_args(EnvAsnTopFiveCallPerc = latex_sanitize(label_percent(0.01)(sum(ENVIRONMENT_ASSIGN_TOP_CALLERS_LATEX$CallPercRaw) / 100)))
```

## Cleanup

```{r, eval = TRUE}
ENVIRONMENT_ASSIGN_TABLE %>%
    mutate(type = str_starts(fun_qual_name, fixed("<NA>"))) %>%
    count(type, wt = calls, name = "calls") %>%
    datatable()

ENVIRONMENT_ASSIGN_TABLE %>%
    count(fun_qual_name, wt=calls, name="calls") %>%
    filter(str_starts(fun_qual_name, fixed("<NA>"))) %>%
    arrange(desc(calls)) %>%
    datatable()
```

## Summary

```{r, eval = TRUE}
ENVIRONMENT_ASSIGN_TABLE %>%
    mutate(same_package = pack_name == result_pack_name) %>%
    group_by(category, same_package) %>%
    summarize(calls = sum(calls)) %>%
    ungroup() %>%
    mutate(call_perc = round(100 * calls / sum(calls), 2)) %>%
    datatable()

ENVIRONMENT_ASSIGN_SUMMARY <-
    ENVIRONMENT_ASSIGN_TABLE %>%
    group_by(fun_name, aliased, category) %>%
    summarize(calls = sum(calls),
              packages = length(unique(pack_name)),
              functions = length(unique(qual_name_2)),
              pack_names = paste(unique(pack_name), collapse = ", "),
              fun_names = paste(unique(qual_name_2), collapse = ", ")) %>%
    ungroup() %>%
    mutate(call_perc = round(100* calls / sum(calls), 2)) %>%
    arrange(desc(calls))

datatable(ENVIRONMENT_ASSIGN_SUMMARY)

EnvAsnUnclassifiedCallCount <- 
    ENVIRONMENT_ASSIGN_TABLE %>%
    filter(is.na(qual_name_2) | str_starts(qual_name_2, fixed("<NA>"))
           | qual_name_2 %in% c("base*$#$*lapply", "base*$#$*eval")) %>%
    pull(calls) %>%
    sum()

EnvAsnUnclassifiedCallPerc <- 
   latex_sanitize(label_percent(0.01)(EnvAsnUnclassifiedCallCount / sum(ENVIRONMENT_ASSIGN_TABLE$calls)))

MacGen$from_args(EnvAsnUnclassifiedCallPerc = EnvAsnUnclassifiedCallPerc)

ENVIRONMENT_ASSIGN_LATEX_TABLE <-
    ENVIRONMENT_ASSIGN_TABLE %>%
    filter(!is.na(qual_name_2) & !str_starts(qual_name_2, fixed("<NA>"))) %>%
    filter(!(qual_name_2 %in% c("base*$#$*lapply", "base*$#$*eval"))) %>%
    group_by(category) %>%
    summarize(CallCnt = sum(calls),
              PackCnt = length(unique(pack_name)),
              FunCnt = length(unique(qual_name_2)),
              pack_names = paste(unique(pack_name), collapse = ", "),
              fun_names = paste(unique(qual_name_2), collapse = ", ")) %>%
    ungroup() %>%
    mutate(CallPerc = latex_sanitize(label_percent()(round(CallCnt / sum(CallCnt), 2)))) %>%
    mutate(CallCnt = label_number_si(accuracy = 0.1)(CallCnt))
    
MacGen$from_df(ENVIRONMENT_ASSIGN_LATEX_TABLE,
               PackCnt,
               FunCnt,
               CallCnt,
               CallPerc, 
               prefix = paste0("EnvAsn", ENVIRONMENT_ASSIGN_LATEX_TABLE$category))
```

## Inner Function Modifications

```{r, eval = TRUE}
ENVIRONMENT_ASSIGN_INNER_FUNCTION_TABLE <-
ENVIRONMENT_ASSIGN_TABLE %>%
filter(category == "User" & str_starts(fun_qual_name, fixed(qual_name_2)))

ENVIRONMENT_ASSIGN_INNER_FUNCTION_TABLE %>%
datatable()

ENVIRONMENT_ASSIGN_USER_NON_R6_COUNT <-
ENVIRONMENT_ASSIGN_TABLE %>%
filter(category == "User" & !str_starts(qual_name_2, fixed("R6"))) %>%
pull(calls) %>%
sum()

EnvAsnUserInnerFunCallPerc <- 
   latex_sanitize(label_percent(0.01)(sum(ENVIRONMENT_ASSIGN_INNER_FUNCTION_TABLE$calls) / ENVIRONMENT_ASSIGN_USER_NON_R6_COUNT))
   
MacGen$from_args(EnvAsnUserInnerFunCallPerc = EnvAsnUserInnerFunCallPerc)


MacGen$from_args(EnvAsnUserInnerFunFunCnt = length(unique(ENVIRONMENT_ASSIGN_INNER_FUNCTION_TABLE$qual_name_2)))
MacGen$from_args(EnvAsnUserInnerFunPackCnt = length(unique(ENVIRONMENT_ASSIGN_INNER_FUNCTION_TABLE$pack_name)))
```

## Core methods package calls

```{r, eval = TRUE}
ENVIRONMENT_ASSIGN_METHODS_CALL_COUNT <-
    ENVIRONMENT_ASSIGN_TABLE %>%
    filter(category == "Core" & str_starts(qual_name_2, fixed("methods*$#$*"))) %>%
    pull(calls) %>%
    sum()

ENVIRONMENT_ASSIGN_CORE_CALL_COUNT <-
    ENVIRONMENT_ASSIGN_TABLE %>%
    filter(category == "Core") %>%
    pull(calls) %>%
    sum()

EnvAsnMethodsCallPerc <- 
   latex_sanitize(label_percent(0.01)(ENVIRONMENT_ASSIGN_METHODS_CALL_COUNT / ENVIRONMENT_ASSIGN_CORE_CALL_COUNT))
   
MacGen$from_args(EnvAsnMethodsCallPerc = EnvAsnMethodsCallPerc)
```
